The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-05 paper.tex
Re-structured first part of intro

Evaluating in a rigorous manner human-robot social interactions is notoriously
difficult~\cite{baxter2016characterising}: studies are either conducted in labs
with constrained protocols to allow for robust measurements and a degree of
replicability, but at the cost of ecological validity. Or on the contrary,
studies are run \emph{in the wild}, which may provide better experimental
realism, but often at the expense of rigorous interaction metrics and replicability.

@@

Studying social interactions requires a social situation that elicits
interactions between the participants.  Such situation is typically scaffolded
by a social task, and consequently, the nature of this task influences in
fundamental ways the kind of interactions that might be observed and analysed.

Because they typically target specific social or cognitive skills in a tightly
controlled manner, traditional socio-cognitive tasks are usually simple,
constrained tasks that do not reflect the complexity and dynamics of real-world
interactions. Conversely, state-of-the-art human-robot interaction aims at
capturing, interpreting and acting upon a rich set of
naturally-occurring social interactions. As such, we argue that further advance
in social human-robot interaction requires us to study and tackle tasks that:

\begin{itemize}
    \item are loosely directed, to maximise natural, non-contrived behaviours;
    \item are long enough and varied enough to elicit a large range of
        interaction situations;
    \item foster rich multi-modal interaction, such as simultaneous speech, gesture, and gaze
        behaviours;
    \item evidence complex social dynamics, such as rhythmic coupling, joint attention,
        implicit turn-taking, a level of unpredictability.
\end{itemize}

The challenge lies in designing a social task that exhibits these features,
while maintaining `good' scientific properties (repeatability, replicability,
robust metrics) as well as good practical properties (not requiring unique or
otherwise very costly experimental environments, not requiring very specific
hardware or robotic platform, easy deployment, short enough experimental
sessions to allow for large groups of participants). So far, our community has
struggled with this endeavour~\cite{baxter2016characterising}.

>>>>

Studying social interactions requires a social \emph{situation} that
effectively elicits interactions between the participants. Such a situation is
typically scaffolded by a social task, and consequently, the nature of this task
influences in fundamental ways the kind of interactions that might be observed
and analysed. In particular, the socio-cognitive tasks commonly found in the
literature of experimental psychology (and HRI) often have a narrow focus:
because they aim at studying one (or a few) specific social or cognitive skill
in isolation and in a controlled manner, these tasks are typically simple and
highly constrained (for instance, an object hand-over task; a perspective-taking
task with cubes, etc.). While these focused endeavours are important and
necessary, we -- as a community -- also acknowledge that these interaction
scenarios do not reflect the complexity and dynamics of real-world
interactions~\cite{baxter2016characterising}, and we certainly observe a strong
trend within our community towards capturing, interpreting and acting upon the rich set of
naturally-occurring social interactions.

Specifically, we believe that further progress in the study of human-robot
interactions should be scaffolded by socio-cognitive challenges that:

\begin{itemize}
    \item are long enough and varied enough to elicit a large range of
        interaction situations;
    \item foster rich multi-modal interaction, such as simultaneous speech, gesture, and gaze
        behaviours;
    \item are loosely directed, to maximise natural, non-contrived behaviours;
    \item evidence complex social dynamics, such as rhythmic coupling, joint attention,
        implicit turn-taking;
    \item include a certain level of non-determinism and unpredictability.
\end{itemize}

The challenge lies in designing a social task that exhibits these features
\emph{while maintaining `good' scientific properties} (repeatability, replicability,
robust metrics) as well as good practical properties (not requiring unique or
otherwise very costly experimental environments, not requiring very specific
hardware or robotic platform, easy deployment, short enough experimental
sessions to allow for large groups of participants).

\subsection{Social play}

@@
